Exploring and understanding the Interdependence of Collaboration Networks

### 2018-10-03 draft.tex
edit2 draft files
new edits

\author{Chakresh Kr. Singh}
\email{chakresh.singh@iitgn.ac.in}
%\affiliation{Indian Institute of Technology, Gandhinagar, India-382355}
\author{Demival Vasques Filho}
\email{d.vasques@auckland.ac.nz}
%\affiliation{University of Auckland, New Zealand}
\author{Dion O' Neale}
\email{d.oneale@auckland.ac.nz}
%\affiliation{University of Auckland, New Zealand}

\author{Shivakumar Jolad}
\email{shiva.jolad@iitgn.ac.in}
%\affiliation{University of Auckland, New Zealand}

@@

@@

\begin{itemize}
	\item What fraction of authors exchange citations but do not co-author?
	\item What fraction of authors co-author but never exchange citations?
	\item How does the above vary with network distance between authors?
	\item What is the response of authors to the citations received?
	\item How does the average network distance change between authors over time?
	\item What is the effect of citations on network distance on co-authorship network and vice-versa?
\end{itemize}

@@

@@

	\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
	\caption{Number of author pairs that co-author but do not cite each other.}
	\label{ftwo}
\end{figure}

@@

	\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
	\caption{Number of author pairs that co-author but do not cite each other.}
	\label{freci}
\end{figure}
\subsubsection{Probability that pairs Co-author given they exchange non-zero citation in the past:}
We define $P(C)$ as probability that they cite each other before collaborating in  $t$ and $P_{n}(c)$ as probability that the pair have cited each $n$ years before collaboration in $t$. 
There fore we have:
\begin{equation}
P(C) = P_{1}(c) + P_{2}(c) + \dots + P_{t-T_0}(c) 
\end{equation}
$T_0$ is time of first co appearance. Let $P(D=1)$ be probability of co-authoring then we have:
\begin{equation}
P(D=1|C) = \frac{P(C|D=1).P(D=1)}{P(C)}
\end{equation}

\subsubsection{Change in average network distance between pairs VS number of citations per pair over time:}
For every Distance matrix $D(t)$ at time t, we measure the distribution of network distances as in fig\ref{f2}. The value of the peak $d^m_{ij}(t)$ for every time, the longest path value $d^l_{ij}(t)$ and the $\bar{d}_{ij}(t)$ at every time step are then plotted against the average number of citations exchanged per pair $\bar{c}$ at time step t.
\begin{equation}
\bar{c} = \frac{\sum_{p_{ij}=1}^{N} C_{p_{ij}} + C_{p_{ji}}}{N} 
\end{equation}
$p_{ij}$ is pair that have non zero mutual citations, $C_{p_{ij}} + C_{p_{ji}}$ is total citations exchanged between $p_{ij}$ and N is number of such pairs.
\section{Results}

>>>>

\author{Chakresh Kr. Singh}
\email{chakresh.singh@iitgn.ac.in}
%\affiliation{Indian Institute of Technology, Gandhinagar, India-382355}
\author{Demival Vasques Filho}
\email{d.vasques@auckland.ac.nz}
%\affiliation{University of Auckland, New Zealand}
\author{Shivakumar Jolad}
\email{shiva.jolad@iitgn.ac.in}
%\affiliation{University of Auckland, New Zealand}

\author{Dion O' Neale}
\email{d.oneale@auckland.ac.nz}
%\affiliation{University of Auckland, New Zealand}

@@

\begin{figure*}[htbp]
	\centering
	\includegraphics[scale = 0.5]{plots/schematic_of_networks}

	\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
	\caption{Diagram of Interdependent citation and co-authorship networks.}
	\label{fi}
\end{figure*}

@@

\begin{itemize}
	\item What fraction of authors exchange citations but do not co-author?
	\item What fraction of authors co-author but never exchange citations?
	\item How does the above vary with network distance between authors?
	\item What is the response of authors to the citations received?
	\item How does the average network distance change between authors over time?
	\item What is the effect of citations on network distance on co-authorship network and vice-versa?
	\item Waiting time distribution for consecutive co-authorship events
	\item Waiting time distribution for consecutive co-citation events
	\item Waiting time in consecutive citations between old and new co-authorship events
\end{itemize}

@@

\begin{figure}
	\centering
	\includegraphics[scale = 0.4]{plots/matrix_schematic}

	\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
	\caption{Schematic diagram showing construction of Data Matrices D and C.}
	\label{fone}
\end{figure}

@@

	\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
	\caption{Number of author pairs that exchange citations but do not co-author}
	\label{ftwo}
\end{figure}

@@

	\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
	\caption{Fraction of returned citations to authors who cite an author. The number lies roughly between 0.4-0.5}
	\label{freci}
\end{figure}
\subsubsection{Probability that pairs Co-author given they exchange non-zero citation in the past:}
We define $P_{ij}(C(t))$ as probability that $j$ cites $i$ at $t$
\begin{equation}
P_{ij}C(t) = \frac{1}{{\cal N}}p_c^i(t)c^j(t)  
\end{equation}
$c^j(t)$ is the fraction of citations $j$ does in year $t$, $p_c^i(t)$ is the probability of $i$ getting cited in year $t$ (this term will consider all the past citations that $i$ has received uptil $t$ ) and ${\cal N}$ is the normalizing factor to ensure summation of probability to be 1. {\color{red}(effect of past citations between i and j?)}

If $t$ is time of first co appearance of $i$ and $j$. Let $P_{ij}(D=1)$ be probability of co-authoring then we have:
\begin{equation}
P_{ij}(D=1|C(t)) = \frac{P_{ij}(C(t)|D=1).P_{ij}(D=1)}{P_{ij}(C(t))}
\end{equation}

\subsubsection{Change in average network distance between pairs VS number of citations per pair over time:}
For every Distance matrix $D(t)$ at time t, we measure the distribution of network distances as in fig\ref{f3}. The value of the peak $d^m_{ij}(t)$ for every time, the longest path value $d^l_{ij}(t)$ and the $\bar{d}_{ij}(t)$ at every time step are then plotted against the average number of citations exchanged per pair $\bar{c}$ at time step t.
\begin{equation}
\bar{c} = \frac{\sum_{p_{ij}=1}^{N} C_{p_{ij}} + C_{p_{ji}}}{N} 
\end{equation}
$p_{ij}$ is pair that have non zero mutual citations, $C_{p_{ij}} + C_{p_{ji}}$ is total citations exchanged between $p_{ij}$ and N is number of such pairs.
\section{Results}
